---
title: "Advanced Rmarkdown"
subtitle: "Workshop-Template-Rmd"
author: "`r paste0('<b>NBIS</b> • ',format(Sys.time(), '%d-%b-%Y'))`"
---

```{r,child="assets/header-lab.Rmd"}
```

Here are some advanced usage of markdown, Rmarkdown and HTML.

# Layout  

Raw HTML can be used to organise content into custom layout.

Use `<div>content</div>` for block content and `<span>content</span>` for inline content. 

For example, here are two blocks:

```
<div>This is content A</div>
<div>This is content B</div>
```

<div>This is content A</div>
<div>This is content B</div>

For paragraphs, use `<p>content</p>`. And use classes `text-left`, `text-center` and `text-right` to align text left, center and right respganise content ectively.

```
<p class="text-right" style="background-color: aliceblue">This content is aligned right.</p>

This is regular paragraph.

<p class="text-center" style="background-color: aliceblue">This content is aligned center.</p>
```

<p class="text-right" style="background-color: aliceblue">This content is aligned right.</p>

This is regular paragraph.

<p class="text-center" style="background-color: aliceblue">This content is aligned center.</p>

<br>

Content can be organised into columns using `pull-left-XX` or `pull-right-XX`. Classes for 30, 40, 50, 60 and 70 have been implemented for left and right. Note that the total width must sum to 100.  

```
<div class="pull-left-50" style="background-color: aliceblue">This content is pulled left.</div>
<div class="pull-right-50 text-center" style="background-color: aliceblue">This content is pulled right and text centered.</div>
```

<div class="pull-left-50" style="background-color: aliceblue">This content is pulled left.</div>
<div class="pull-right-50 text-center" style="background-color: aliceblue">This content is pulled right and text centered.</div>  

<br>

```
<div class="pull-left-30" style="background-color: aliceblue">This content is pulled left.</div>
<div class="pull-right-70" style="background-color: aliceblue">This content is pulled right.</div>
```

<div class="pull-left-30" style="background-color: aliceblue">This content is pulled left.</div>
<div class="pull-right-70" style="background-color: aliceblue">This content is pulled right.</div>  

<br>

This is an example of nested columns.  

```
<div class="pull-left-30" style="background-color: aliceblue">This column is pulled left.</div>
<div class="pull-right-70" style="background-color: aliceblue">
This column is pulled right.
<div class="pull-left-50" style="background-color: #d0ece7">
Nested left.
</div>
<div class="pull-right-50" style="background-color: #f2d7d5">
Nested right.
</div>
</div>
```

<div class="pull-left-30" style="background-color: aliceblue">This column is pulled left.</div>
<div class="pull-right-70" style="background-color: aliceblue">
This column is pulled right.
<div class="pull-left-50" style="background-color: #d0ece7">
Nested left.
</div>
<div class="pull-right-50" style="background-color: #f2d7d5">
Nested right.
</div>
</div>

<br>

# Extras

These are features implemented in this workshop material.

## Icons

Icons can be placed directly into md or Rmd using HTML i-tag.

`<i class="fas fa-lightbulb"></i>` <i class="fas fa-lightbulb"></i>

Icons can also be placed programatically through R using the R package [fontawesome](https://github.com/rstudio/fontawesome).

`` `r "\u0060r fontawesome::fa('lightbulb')\u0060"` ``

`r fontawesome::fa("lightbulb")`

Optional arguments are height and fill.

`` `r "\u0060r fontawesome::fa('lightbulb',height='30px',fill='steelblue')\u0060"` ``

`r fontawesome::fa("lightbulb",height='30px',fill='steelblue')`

For full list of icons check out [FontAwesome](https://fontawesome.com/icons).

## Boxes

Highlighted instruction boxes can be created using a div with class `boxy`.

```
<div class="boxy">
This is some instruction.
</div>
```

<div class="boxy">
This is some instruction.
</div>

Adding an icon to the box.

```
<div class="boxy boxy-lightbulb">
This is some instruction.
</div>
```

<div class="boxy boxy-lightbulb">
This is some instruction.
</div>

Currently implemented icons for boxes are `boxy-lightbulb` (<i class="fas fa-lightbulb"></i>) for tips, `boxy-exclamation` (<i class="fas fa-exclamation"></i>) for note, `boxy-clipboard-list` (<i class="fas fa-clipboard-list"></i>) for tasks, `boxy-comments` (<i class="fas fa-comments"></i>) for discuss, `boxy-desktop` (<i class="fas fa-desktop"></i>) for desktop/local and `boxy-cloud` (<i class="fas fa-cloud"></i>) for cloud.

An optional orange colour can be used for warning/optional content.

```
<div class="boxy boxy-orange">
**Optional**  
This is some instruction.
</div>
```

<div class="boxy boxy-orange">
**Optional**  
This is some instruction.
</div>

Adding an icon to the box.

```
<div class="boxy boxy-exclamation boxy-orange">
**Optional**
This is some instruction.
</div>
```

<div class="boxy boxy-exclamation boxy-orange">
**Optional**  
This is some instruction.
</div>

## Block title

The code language can be displayed above input code by setting `block.title=TRUE`.

It can be placed above source block with output.

```{r,echo=FALSE,comment=""}
cat(paste0("```{r,block.title=TRUE}\n","Sys.Date()\n","``` \n"))
```

```{r,block.title=TRUE}
Sys.Date()
```

Or it can be placed above source block without output.

```{r,echo=FALSE,comment=""}
cat(paste0("```{r,block.title=TRUE,eval=FALSE}\n","Sys.Date()\n","``` \n"))
```

```{r,block.title=TRUE,eval=FALSE}
Sys.Date()
```

Or above output block if the source is hidden. In this case, the title changes to OUTPUT.

```{r,echo=FALSE,comment=""}
cat(paste0("```{r,block.title=TRUE,echo=FALSE}\n","Sys.Date()\n","``` \n"))
```

```{r,block.title=TRUE,echo=FALSE}
Sys.Date()
```

For instruction, it might be necessary to run some code and print the output as input-source-code. `echo=FALSE` hides the source code. `comment=""` hides the `##` from print statements. `class.output="r"` code highlights the output block.

```{r,echo=FALSE,comment=""}
cat(paste0("```{r,block.title=TRUE,echo=FALSE,comment='',class.output='r'}\n","cat('Sys.Date()')\n","``` \n"))
```

```{r,block.title=TRUE,echo=FALSE,comment='',class.output='r'}
cat("Sys.Date()")
```

## Accordion

Code can be hidden for interactive display using `accordion=TRUE`.

```{r,echo=FALSE,comment=""}
cat(paste0("```{r,accordion=TRUE}\n","Sys.Date()\n","``` \n"))
```

The above code creates the button below.

```{r,accordion=TRUE}
Sys.Date()
```

<i class="fas fa-exclamation-circle"></i> Note that contents inside the accordion will NOT be printed (when minimised) on converting this HTML to PDF. Expanded accordion block will be printed when converting to PDF.

If the accordion block is to contain regular text and code block, then the raw HTML code needs to be used. Below is an example.

````markdown
<div class="boxy boxy-clipboard-list">

**Challenge**

If I create a vector as follows `x <-c(5,3,9,"6")`, what is the "type" of the element in the third position? Is it a number?

<p>
<button class="btn btn-sm btn-primary btn-collapse btn-collapse-normal collapsed" type="button" data-toggle="collapse" data-target="#task-vectors" aria-expanded="false" aria-controls="task-vectors">
</button>
</p>
<div class="collapse" id="task-vectors">
<div class="card card-body">

```{r}
x <-c(5,3,9,"6")
typeof(x[3])
```

<i class="fas fa-lightbulb"></i> The third position is not a number, it's a character. In fact, all elements in this vector are characters. If there is a character in a numeric vector, all elements are converted to characters (`typeof(x)`).

</div>
</div>
</div>
````

The above code creates the block below. Note that the variable `task-vectors` (used in 3 positions above) needs to changed to a unique value for each such block in a document.

<div class="boxy boxy-clipboard-list">

**Challenge**  

If I create a vector as follows `x <-c(5,3,9,"6")`, what is the "type" of the element in the third position? Is it a number?

<p>
<button class="btn btn-sm btn-primary btn-collapse btn-collapse-normal collapsed" type="button" data-toggle="collapse" data-target="#task-vectors" aria-expanded="false" aria-controls="task-vectors">
</button>
</p>
<div class="collapse" id="task-vectors">
<div class="card card-body">

```{r}
x <-c(5,3,9,"6")
typeof(x[3])
```

<i class="fas fa-lightbulb"></i> The third position is not a number, it's a character. In fact, all elements in this vector are characters. If there is a character in a numeric vector, all elements are converted to characters (`typeof(x)`).

</div>
</div>
</div>

***
